The four years of my DPhil studies have been the most difficult, frustrating, yet simultaneously stimulating and bittersweet period of my life. 
This journey would not have been possible without the support of many individuals, and I would like to take this unique opportunity to express my heartfelt gratitude.

First and foremost, I wish to thank my supervisors, Prof. Xianguo Lu and Prof. Dave Wark. 
Xianguo's invaluable insights and steadfast guidance formed the backbone of my DPhil research. 
Dave's unwavering encouragement—and his guitars—helped me through challenging times.

I am privileged to have been part of the wonderful T2K collaboration, through which I have received immense support and warmth. 
Firstly, I would like to thank the SFGD assembly team—Dr. Chien Lin, Dr. Hikaru Tanigawa, Jiayu Ji, Abraham Teklu, Kuunal Mahtani, Dr. Ciro Riccio, Dr. Tristan Doyle, Dr. Aleksandr Mefodev, Prof. Tsunayuki Matsubara, and many others—for the unforgettable experiences of pulling fishing lines and inserting metal rods. 
Secondly, the outstanding work of my colleagues, Dr. Aoi Eguchi, Dr. Xingyu Zhao, soon-to-be Dr. Katharina Lachner, and Dr. Alexander Izmaylov, has significantly contributed to the success of my research. 
Thirdly, I am deeply grateful for the invaluable advice and mentorship of senior members, including Prof. Davide Sgalaberna, Dr. Stephen Dolan, Prof. Deborah Harris, Prof. Kevin McFarland, Dr. Clarence Wret, Dr. Sam Jenkins, Dr. Joe Walsh, Dr. Stefania Bordoni, and Dr. Ryosuke Akutsu, all of whom have been critical to the progress of my work.

Beyond T2K, I have been fortunate to work with my GENIE colleagues—Prof. Constantinos Andreopoulos, Dr. Marco Roda, and Dr. Julia Tena-Vidal—whose indispensable support has been vital to the tuning project and my understanding of the \genie generator.

I am also lucky to be part of the incredible accelerator group at Oxford. My heartfelt thanks go to its members for their cheerful camaraderie and enlightening discussions: Giles, Morgan, Kirsty, Lawrence, Ciaran, Soniya, Dan, Tom, Federico, John, Lars, Abbey, and Yiwen.

Outside the neutrino research community, the joyful moments and leisurely conversations with my friends back home have been a wellspring of energy throughout this arduous journey. This experience would not have been possible without the unwavering emotional and financial support of my family and relatives.

I owe a special debt of gratitude to my aunt and uncle, whose selfless support and guidance during my early education laid the foundation for my research career. My appreciation for my parents cannot be overstated; they have always prioritised my education and respected my decisions.

Finally, my deepest thanks go to my partner, Dr. Chenyi Zhang, whose smile is like warm sunshine on gloomy British winter days. Thinking of all the wonderful memories we have shared brings an irrepressible smile to my face, and I look forward to creating many more in the years to come.
